DPIV Analysis and Real Time Implementation

### 2023-01-06 Paper/main.tex
adding comments in section results

The micro-particles hydrodynamic response in frequency domain was evaluated by computing the spectrum of $\meann$ in the two components $\abscissa$ and $\ordinate$. This provides informations on the frequency components involved in the dynamic process in terms of fundamental frequency, imposed by the hydrodynamic input and to investigate possible high-frequency components to be associated with intrinsic micro-particles behaviors.
\\The second analysis that this platform provides is the counting particles one (\fig\ref{Algorithms} block (9)). This procedure is based on highlighting the particles in the image distinguishing them from the background. It provides a continuous counting in the time of the micro-particles number in the investigated area, avoiding any manual and individual selecting of the frames to be studied \DS{Although current approaches rely on manual counting or others, (add references if any) the provided implementation makes use of a counting algorithm ...}. It allows to analyze the video frame by frame, count the number of particles and collect this information in a signal. This last can also be averaged over time to obtain a single average particles number for a given experimental condition.
\\The counting procedure is essential not only to have an idea of the number of micro-particles involved in the process, but, even more, when we want to compare the results obtained with different types of particles. The velocity obtained by the DPIV-based algorithm, in fact, can be strongly influenced by the number of particles present in the ROI since a spatial average is considered. It should also be considered that different micro-particles correspond to different densities which influence the number of them in the process. According to what has been said, it is necessary to normalize the velocity signals for the average particles number when we wants to compare processes characterized by micro-particles of different nature and physical properties.
\\Having selected the ROI, the counting operation follows some steps all based on image processing as presented in \MANU{Add reference}. A first conversion of the selected image portion to greyscale is followed by a duplication of the image. A Gaussian filter is applied and the resulting filtered image is subtracted from the greyscale one. A binarization procedure of the resulting image is performed.

@@

\section{Results and discussion}
In this chapter the experimental results are presented. In particular in \sect\ref{sec:suspended-particles} we will discuss the behavior of synthetic particles related to the fluid in which they are suspended and in \sect\ref{sec:comparison} we will compare the hydrodynamic response of the different types of cells, viable and dead, and synthetic particles. Referring to the methodology as you did if you like. \sect\ref{sec:OnlineOffline} shows a comparison of the results obtained with the two implementations.
Since the micro-particles are induced to move in the horizontal direction, this will be the velocity component considered in the subsequent analysis. 
%Looking at the movement of the micro-particles along the micro-channel and considering also the image orientation, the dominant velocity component is the horizonatal one. In fact, the trend of the horizontal velocity component $<V_x(t)>$ shows the periodicity of the oscillating input flow imposed. This component is the one taken in consideration for the following analysis.

@@

The described algorithm was used to study how the hydrodynamic response of synthetic micro particles, silica beads, can be related to their physical properties and differ according to the fluid in which they are suspended. To compare the results obtained for the same kind of particles suspended in different fluids, the velocity signal $\mean{x}$ was computed per each experiment, by the DPIV-based algorithm described in \sect\ref{sec:method}.

\begin{figure}[t]
\centering
    \begin{subfigure}[b]{\columnwidth}
    \centering
	\includegraphics[width=1\columnwidth]{images/BeadsA}
	\caption{}
	\label{A}
    \end{subfigure}
    \begin{subfigure}[b]{\columnwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/BeadsB}
	\caption{}
	\label{B}
    \end{subfigure}
    \begin{subfigure}[b]{\columnwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/BeadsC}
	\caption{}
	\label{C}
    \end{subfigure}
    \begin{subfigure}[b]{\columnwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/BeadsD}
	\caption{}
	\label{D}
    \end{subfigure}
\centering{\caption{\label{Beads}The velocity trends $\mean{x}$ and its spectrum obtained in the experimental condition with $\amplitude=0.1~\flow$ and  $\frequency=0.1~\hertz$: velocity signal (a) and its spectrum (b) of silica beads in PBS solution and velocity signal (c) and its spectrum (d) of silica beads in glycerol-water solution.}}
\end{figure}

@@

In ~\fig\ref{Beads}, for silica beads in PBS and in glycerol-water solution, in the experimental condition with $\amplitude=0.1~\flow$ and  $\frequency=0.1~\hertz$, the velocity signals in the dominant component  $<V_x(t)>$ and their spectrum are plotted.
It can be noted that the speed signal relating to the silica beads sample in the PBS solution (see ~\fig\ref{Beads}(a)) is noisier than the speed signal relating to the silica beads sample in the glycerol-water solution (see ~\fig\ref{Beads}(c)). This is given by the fact that since the silica beads have a higher density than PBS, they tend to settle in the bottom of the micro channel, putting up resistance to the imposed hydrodynamic actuation at the input. Suspended beads in a solution of the same density have shown to be an effective solution to this problem. This allows beads to float in the fluid and not to pose resistance to the hydrodynamic input that is imposed. The speed signal relating to the silica beads sample in the glycerol-water solution (see ~\fig\ref{Beads}(c)) shows a shape similar to that expected from the input flux supplied, a sine wave with frequency $\frequency=0.1~\hertz$, detected from the fundamental frequency in the spectrum, and amplitude $\amplitude=0.1~\flow$.
\\The micro-particles hydrodynamic response in time domain was evaluated by computing the range of the velocity signal $\mean{x}$, as shown in \eqn (\ref{eqn:range}). ~\fig\ref{BeadsFinal} shows the value of $\range$ and the amplitude peak at the fundamental frequency, $\peak$, for each experimental condition. The two curves are related to silica beads in the two different solutions considered and each point of the curves is correlated to the amplitude of the external oscillating input flow strength $\amplitude$ with a constant $\frequency=0.1~\hertz$. 
\\The curve related to the beads in PBS does not show any correlation between the imposed input and the hydrodynamic response of the micro-particles. The curve relating to the beads in the glycerol-water solution shows how the parameters examined in the time domain and in the frequency domain increase as the input amplitude increases, showing a correlation between the input and the hydrodynamic response of the micro-particles.
Since silica beads are synthetic particles, what we expect is that they do not provide any resistance to the input sources and so the glycerol solution is the most suitable among the analyzed ones because it allows to show up this behavior.
For this reason, in \sect\ref{sec:comparison} in which the comparison between synthetic particles, live cells and cells exposed to death stimuli is made, and in \sect\ref{sec:OnlineOffline} in which the results obtained from the online and offline platform are compared, only the results relating to silica beads in the glycerol-water solution will be considered beacause they allowed a better process characterization.

>>>>

The micro-particles hydrodynamic response in frequency domain was evaluated by computing the spectrum of $\meann$ in the two components $\abscissa$ and $\ordinate$. This provides informations on the frequency components involved in the dynamic process in terms of fundamental frequency, imposed by the hydrodynamic input and to investigate possible high-frequency components to be associated with intrinsic micro-particles behaviors\DS{I wouldn't use fundamental frequency. I'd rather stress the fact that it comes from the input signal }.
\\The second analysis that this platform provides is the counting particles one (\fig\ref{Algorithms} block (9)). The procedure is based on highlighting the particles in the image distinguishing them from the background. It provides a continuous counting in the time of the micro-particles number in the investigated area, avoiding any manual and individual selecting of the frames to be studied \DS{Although current approaches rely on manual counting or others, (add references if any) the provided implementation makes use of a counting algorithm ...}. It allows to analyze the video frame by frame, count the number of particles and collect this information in a signal. This last\DS{The latter} can also be averaged over time to obtain a single average particles number for a given experimental condition.
\\The counting procedure is essential not only to have an idea of the number of micro-particles involved in the process, but, even more, when we want to compare the results obtained with different types of particles\DS{The structure "when we want" is not that formal. Try to rewrite this sentence}. The velocity obtained by the DPIV-based algorithm, in fact, can be strongly influenced by the number of particles present in the ROI since a spatial average is considered. It should also be considered that different micro-particles correspond to different densities which influence the number of them in the process. According to what has been said, it is necessary to normalize the velocity signals for the average particles number when we wants to compare processes characterized by micro-particles of different nature and physical properties\DS{Try to be more formal and try to shrink a little bit this period about the normalization. }.
After the ROI selection, the counting operation follows some steps all based on image processing as presented in \MANU{Add reference}. A first conversion of the selected image portion to greyscale is followed by a duplication of the image. A Gaussian filter is applied and the resulting filtered image is subtracted from the greyscale one. A binarization procedure of the resulting image is performed.

@@

\section{Results and discussion}
In this chapter\DS{section} the experimental results are presented. In particular in \sect\ref{sec:suspended-particles} we will discuss the synthetic particles behavior related to the fluid in which they are suspended and in \sect\ref{sec:comparison} we will compare the hydrodynamic response of the different types of cells, viable, dead, and synthetic particles. \sect\ref{sec:OnlineOffline} shows a comparison of the results obtained with the two implementations presented in \sect{\ref{sec:method}}, i.e. online and offline implementations.
Since micro-particles are mostly induced to move horizontally due to the input flow, this velocity component will be analyzed in the following analysis.
%Looking at the movement of the micro-particles along the micro-channel and considering also the image orientation, the dominant velocity component is the horizonatal one. In fact, the trend of the horizontal velocity component $<V_x(t)>$ shows the periodicity of the oscillating input flow imposed. This component is the one taken in consideration for the following analysis.

@@

The described algorithm was used to study how the hydrodynamic response of synthetic micro particles, i.e. silica beads, can be related to their physical properties and differ according to the fluid in which they are suspended. To compare the results obtained for the same kind of particles suspended in different fluids, the velocity signal $\mean{x}$ was computed per each experiment, by the DPIV-based algorithm described in \sect\ref{sec:method}.

\begin{figure}[t]
\centering
    \begin{subfigure}[b]{\columnwidth}
    \centering
	\includegraphics[width=1\columnwidth]{images/BeadsA}
	\caption{}
	\label{A}
    \end{subfigure}
    \begin{subfigure}[b]{\columnwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/BeadsB}
	\caption{}
	\label{B}
    \end{subfigure}
    \begin{subfigure}[b]{\columnwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/BeadsC}
	\caption{}
	\label{C}
    \end{subfigure}
    \begin{subfigure}[b]{\columnwidth}
	\centering
	\includegraphics[width=1\columnwidth]{images/BeadsD}
	\caption{}
	\label{D}
    \end{subfigure}
\centering{\caption{\label{Beads}The velocity trends $\mean{x}$ and its spectrum obtained in the experimental condition with $\amplitude=0.1~\flow$ and  $\frequency=0.1~\hertz$: velocity signal (a) and its spectrum (b) of silica beads in PBS solution and velocity signal (c) and its spectrum (d) of silica beads in glycerol-water solution.\DS{add 0.1 in the matlab plot for figure (b) and (d)}}}
\end{figure}

@@

In ~\fig\ref{Beads}, for silica beads in PBS and in glycerol-water solution, in the experimental condition with $\amplitude=0.1~\flow$ and  $\frequency=0.1~\hertz$, the velocity signals in the dominant component  $<V_x(t)>$ and their spectrum are plotted.
It can be noted that the speed signal relating to the silica beads sample in the PBS solution (see ~\fig\ref{Beads}(a)) is noisier than the speed signal relating to the silica beads sample in the glycerol-water solution (see ~\fig\ref{Beads}(c)). This is given by the fact that since the silica beads have a higher density than PBS, they tend to settle in the bottom of the micro channel, putting up resistance to the imposed hydrodynamic actuation at the input. Suspended beads in a solution of the same density have shown to be an effective solution to this problem. As a result, the hydrodynamic input exerted on the fluid has no effect on the beads' ability to float freely and the speed signal relating to the silica beads sample in the glycerol-water solution (see ~\fig\ref{Beads}(c)) shows a shape similar to the input flow supplied, i.e. a sine wave with frequency $\frequency=0.1~\hertz$. In addition, such frequency can be detected from the spectrumv\DS{add ref picture}, and amplitude $\amplitude=0.1~\flow$.
\\The micro-particles hydrodynamic response in time domain was evaluated by computing the range of the velocity signal $\mean{x}$, as shown in \eqn (\ref{eqn:range}). ~\fig\ref{BeadsFinal} shows the value of $\range$ and the amplitude peak at the fundamental frequency, $\peak$, for each experimental condition. The two curves are related to silica beads in the two different solutions considered and each point of the curves is correlated to the amplitude of the external oscillating input flow strength $\amplitude$ with a constant $\frequency=0.1~\hertz$. 
\\The curve related to the beads in PBS does not show any correlation between the imposed input and the hydrodynamic response of the micro-particles. The curve relating to the beads in the glycerol-water solution shows how the parameters examined in the time domain and in the frequency domain increase as the input amplitude increases, showing a correlation between the input and the hydrodynamic response of the micro-particles.
Since silica beads are synthetic particles, what we expect is that they do not provide any resistance to the input sources and so the glycerol solution is the most suitable among the analyzed ones because it allows to show up this behavior.
For this reason, in \sect\ref{sec:comparison} in which the comparison between synthetic particles, live cells and cells exposed to death stimuli is made, and in \sect\ref{sec:OnlineOffline} in which the results obtained from the online and offline platform are compared, only the results relating to silica beads in the glycerol-water solution will be considered beacause they allowed a better process characterization.
